\documentclass[letterpaper,10pt]{article}


%A Few Useful Packages


\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}


%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}


%--------------------BEGIN DOCUMENT----------------------
\begin{document}


%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{ \Huge  Ziqing \textsc{Zhao}
	}\bigskip\par}
	


Dear hiring manager,

I was greatly attracted by the full-time associate analyst job in Axtria posting on Handshake. Your recruiting team and I had a great conversation during the recent career fair and the information session at Cornell. Overall, I am familiar with the tools I shall be using and the field I shall be in, I learn new things quickly, and the previous internship well equipped me experiences of dealing with industrial data and working with people in various settings. Thus, I think I am a good fit for this job.

A Purdue Econometrics graduate with minor in statistics and a current Cornell Applied Statistics master student, I learned my quantitative skills the hard way -- through rigorous training and research. Software namely SAS and Minitab, and languages including Python, R, and SQL were used extensively during my previous study. In the passing summer, I worked as a research assistant in Prof. Xi Kathy Zhou Lab at Weill Cornell Medical College, constructing databases from heterogeneous data to study the relationship between fructose intake and colon cancer. For my undergraduate honor thesis, I wrote Python scripts to parse data from media web pages and employed mathematical and statistical tools to study the optimal decisions of NBA players choosing teams for the next season. This project was later presented on the Undergraduate Research Conference and awarded as the (only) distinguished thesis in the college.

Of course I like to explore unknown, to face challenge, and to solve problems independently. But I am also very much of a team worker. Last year, I interned in Montagne Medical Device Cooperation, where I was in charge of using Minitab to monitor sterilization process by applying six sigma methodology, and providing statistical insights on the level and consistency of the product quality based on data visualization. I also presented on  weekly meetings with the process engineer team and explained the key terms and concepts to those who were less familiar. This experience, along with my experience as a Teaching Assistant for Econometrics, taught me how to be comfortable at every corner of the meeting desk. Hopefully, I wouldn’t shy away from raising questions and contributing thoughts during my first meetings in Axtria.

I am anticipating to go through the training sessions at the beginning of my career pretty smoothly. Not only because of the skills I have, but also my ability to learn things quickly. Here at Cornell, I am so obsessed with CS courses like Machine Learning for Intelligent Systems in Python, and self-learning packages like TensorFlow. I’m thrilled to explore the mathematics behind machine learning and really know how it works. 

Thanks for your time and consideration. I would appreciate the chance to further discuss my application. I look forward to further discussing this opportunities.


\end{document}